---
title: "searchConsoleR demo"
author: "Mark Edmondson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Links

[Google Search Console](http://www.google.com/webmasters/tools/)

[Search Console v3 API docs](https://developers.google.com/webmaster-tools/)

## Function Quick Guide

### Search analytics
* search_analytics() - download Google SEO data into an R dataframe.

### Website admin
* list_websites() - list websites in your Google Search Console.
* add_website() - add a website to your Google Search Console.
* delete_website() - delete a website from your Google Search Console.

### Sitemaps
* list_sitemaps() - list sitemaps recognised in Google Search Console.
* add_sitemap() - add sitemap URL location to Google Search Console.
* delete_sitemap() - remove sitemap URL location in Google Search Console.

### Error listings
* crawl_errors() - list various types of crawl errors googlebot has found.
* list_crawl_error_samples() - get a list of example URLs with errors.
* error_sample_url() - show details about an example URL error (for example, links to a 404 URL)
* fix_sample_url() - make a URL as fixed.

### Authentication functions
* scr_auth() - main authentication function. Works locally and within a Shiny environment.
* getShinyURL() - detects the Shiny domain URL. Needed for authentication flow.
* shinygaGetTokenURL() - Imported from shinyga() package. Needed for authentication flow, gives the URL a user must click on to get verified.

## Guide

Install searchConsoleR from github using devtools.

```
devtools::install_github("MarkEdmondson1234/searchConsoleR")
library(searchConsoleR)
```

Work flow always starts with authenticating with Google.
```
scr_auth()
```

Your browser window should open up and go through the Google sign in OAuth2 flow. Verify with a user that has Search Console access to the websites you want to work with.

Check out the documentation of any function for a guide on what else can be done.
```
?scr_auth
```

If it works, you should see a list of your websites in the Search Console via:

```
sc_websites <- list_websites()
sc_websites
```

We'll need ```sc_websites$siteUrl``` for the majority of the other functions.

Most people will find the search analytics most useful.  All methods from the web interface are available.  Here is an example query:

```
gbr_desktop_queries <- 
    search_analytics("http://example.com", 
                     "2015-07-01", "2015-08-01", 
                     c("query", "page"), 
                     dimensionFilterExp = c("device==DESKTOP","country==GBR"), 
                     searchType="web", rowLimit = 100)
```


## dimensionFilterExp

Filter your API results using this format: ```filter operator expression```

Filter can be one of:

* 'country',
* 'device'
* 'page'
* 'query')

Operator can be one of ```~~, ==, !~, !=``` where the symbols mean:

* `~~` : 'contains',
* `==` : 'equals',
* `!~` : 'notContains',
* `!=` : 'notEquals')

Expression for page or query if freeform.

Expression for country must be the three letter country code as per the [the ISO 3166-1 alpha-3] standard. e.g. GBR

Expression for device must be one of:

* 'MOBILE'
* 'DESKTOP'
* 'TABLET'

You can have multiple AND filters by putting them in a character vector.  

```
c("device==DESKTOP","country==GBR")
```

OR filters aren't supported yet in the API.


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
